Finite and Infinite Games

### 2014-06-24 miscellaneous/unorganized/2014-06-24-auburnGameTheoryTalk.tex
minor changes to lamar talk for AU REU talk

\subtitle
{at Lamar University} % (optional)

@@

\date[14-06-09] % (optional)
{June 9, 2014}

@@

\section{Before We Begin...}

\begin{frame}{Grad School!}
  \begin{itemize}
    \item I entered graduate school at Auburn in 2008. Planned on doing
          two Masters in Math and Math Ed. Quickly switched to just Math,
          and I'm finishing up my dissertation on topological games
          to defend this fall or spring.
    \pause
    \item Kind of stumbled into my program. Worked for me, but I feel lucky!
    \pause
    \item I highly recommend graduate school in math - but keep your mind on
          your end career goal (Academia? Industry?)
  \end{itemize}
\end{frame}

\begin{frame}{Preparing for Grad School}
  \begin{itemize}
    \item Think about what you want to study. You're no longer a ``math major'',
          you'll be a graph theorist, or topologist, or algebraist.
    \pause
    \item Find professors that do what you want to study. You'll be picking
          an advisor to work with for a while. (Or, consider getting a Masters
          before PhD to get your feet wet.)
    \pause
    \item Make sure there's Graduate Assistantships available. At Auburn,
          being a GA waives tuition and gives you a paycheck.
          \textbf{Don't go into debt for grad school!}
    \pause
    \item Check website for other requirements. (Math GRE? Required letters?
          Deadlines?)
  \end{itemize}
\end{frame}

\begin{frame}{What's being a Grad Student like?}
  \begin{itemize}
    \item Classes... at first. Hopefully, only classes you're interested in!
    \pause
    \item More free time... to study or research.
    \pause
    \item Get involved! Connect with other grad students outside your
          department. Serving grad student gov't is worthwhile too.
    \pause
    \item Go to conferences. Students often can get funding to cover costs,
          you get to travel, and learn what's happening at other schools.
    \pause
    \item Teach and give talks. Being able to communicate your work is as
          important as actually doing it.
  \end{itemize}
\end{frame}

@@

  We've just seen that every sequence of the form $\<4,11,6,5,7,3,2,\dots\>$
  is in $W$, since $\pl A$ wins those playthroughs of the game.
  (Actually, another puzzle: show that all sequences of the form
  $\<4,11,6,5,7,\dots\>$ are in $W$.)

@@

\begin{frame}{Who wins?}
  \begin{theorem}
    $\pl B$ has a winning strategy in Convergence Game $A=\{a_0,a_1,\dots\}$
    (that is, when $A$ is a ``countable'' set).
  \end{theorem}
\end{frame}

@@

  \begin{theorem}
    The real numbers $\mathbb{R}$ cannot be written in a list
    $\{r_0,r_1,\dots\}$ (they are ``uncountable'').
  \end{theorem}

  \begin{proof}
    Every increasing bounded above sequence converges to a real number
    (see Cal II). Thus $\pl A$ always wins the Convergence Game $A=\mathbb{R}$.

    But since $\pl B$ wins if $A$ is a countable set which can be written like
    $\{a_0,a_1,\dots\}$, we know that $\mathbb{R}$ cannot be countable.
  \end{proof}
\end{frame}

>>>>

\subtitle
{Auburn REU Presentation} % (optional)

@@

\date[14-06-24] % (optional)
{June 24, 2014}

@@

@@

  We've just seen that every sequence of the form $\<4,11,6,5,7,3,2,\dots\>$
  is in $W$, since $\pl A$ wins those playthroughs of the game.

@@

\begin{frame}{Who wins?}
  \begin{theorem}
    $\pl B$ has a winning strategy in Convergence Game when $A$ can be indexed
    by the non-negative integers: $A=\{a_0,a_1,a_2,\dots\}$
    (that is, when $A$ is a \term{countable} set).
  \end{theorem}
\end{frame}

@@

  \begin{theorem}
    The real numbers $\mathbb{R}$ cannot be exhaustively indexed by the
    non-negative integers (they are \term{uncountable}).
  \end{theorem}

  \begin{proof}
    Every increasing bounded above sequence converges to a real number
    (see Cal II). Thus $\pl A$ has a winning strategy for
    the Convergence Game $A=\mathbb{R}$.

    But since $\pl B$ has a winning strategy when $A$ is a countable set, we've
    proven that $\mathbb{R}$ cannot be countable.
  \end{proof}
\end{frame}
